Environment affects specialisation of plants and pollinators

### 2019-11-30 paper/manuscript.Rmd
Last couple sentences of introduction

Here, we investigate whether and how environmental stress can systematically affect specialisation.  
Our main aim is to test the two aforementioned hypotheses that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
In other words we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community [which has been previously shown to be determinant factor; @gravel_bringing_2018]
We test these hypotheses using data on plant-pollinator interactions. 
This system is a particularly interesting XX.
We use the species' patterns of global occurrence to estimate the bioclimatic suitability of their communities and use this as an indirect measure of the environmental stress they might experience.

>>>>

Here, we investigate whether and how environmental stress can systematically affect specialisation.  
Our main aim is to test the two aforementioned hypotheses that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
In other words we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community [which has been previously shown to be determinant factor; @gravel_bringing_2018]
We test these hypotheses using data on plant-pollinator interactions. 
These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species respond to environmental stress given the available partners.
We estimate the stress species might experience in their community by calculating the the bioclimatic suitability of their communities given the species' patterns of global occurrence.
